cell-type-neuroblastoma-04 Analysis

### 2025-06-11 analyses/cell-type-neuroblastoma-04/notebook-template.Rmd
initiate template with a barebones readme

---
title: "infercnv-consensus-cell-type Analysis"
author:
  - Your name here
date: "`r Sys.Date()`"
output: html_notebook
---

@@

# The path to this module
module_base <- file.path(repository_base, "analyses", "infercnv-consensus-cell-type")
```

>>>>

---
title: "cell-type-neuroblastoma-04 Analysis"
author:
  - Your name here
date: "`r Sys.Date()`"
output: html_notebook
---

@@

# The path to this module
module_base <- file.path(repository_base, "analyses", "cell-type-neuroblastoma-04")
```
